---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rd3fc)](https://cran.r-project.org/package=rd3fc)

### Install

```
devtools::install_github("timelyportfolio/rd3fc")
```

### Example

`quantmod` is an superpower of R.  Let's remember how few lines of code we need to make a static candlestick chart.

```{r warning=FALSE, message=FALSE}
library(quantmod)

getSymbols("^GSPC", from = "2016-12-31")
chart_Series(GSPC)
```

I view this as simply amazing, but the only thing missing is some interactivity.  `rd3fc` plans to eventually complete translate `chart_Series` to an interactive chart, but for now it will just produce the candlestick.

```
library(rd3fc)
# will use the current.chob() if no arguments
chartseries()
```

[live example](https://bl.ocks.org/timelyportfolio/5ab93494dedad6e5a79a07bbb3a78ecd)

### Code of Conduct

I would love help ad ideas, but please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.


### Attribution and Thanks

Thanks to Mike Bostock for [`d3.js`](https://d3js.org) and the team at [Scott Logic](http://www.scottlogic.com/) for [`d3fc`](https://d3fc.io).
